Optimal Symmetric Multimodal Templates and Concatenated Random Forests for Supervised Brain Tumor Segmentation (Simplified) with \textit{ANTsR}

### 2014-05-01 paper.tex
ENH: 1st sent in abstract

\begin{abstract} 
Automated brain tumor segmentation in MRI is complicated by the lack
of prior knowledge concerning tumor location, spatial extent, shape,
possible displacement of normal tissue, and intensity signature.
These factors limit the applicability of techniques with established
performance in related tasks such as normal brain tissue
segmentation.  To alleviate the limitations of traditional tissue
classification, we introduce a symmetric template-based framework for supervised
segmentation based on multiple modality intensity, geometry and asymmetry feature sets.  These features drive a supervised whole-brain and tumor segmentation
approach based on random forest-derived probabilities.  The
asymmetry-related features, in particular, 
demonstrate excellent discriminative properties within this framework. 
We also gain performance by alternately generating
probability maps from random forest models and feeding these maps 
into Markov random field regularized probabilistic segmentation.  This
strategy allows us to interface the supervised learning capabilities of the random forest
model with regularized probabilistic segmentation.  The newly
developed \textit{ANTsR} open source software package facilitates
the proposed methodology.  \textit{ANTsR} is a comprehensive interface between the
popular Advanced Normalization Tools (ANTs) and the \textit{R}
statistical project. \textit{ANTsR} integrates proven image analysis methods
for image registration, segmentation, bias correction, and
template building with \textit{R}'s statistical and machine
learning techniques and state-of-the-art visualization possibilities.  
The reported algorithmic framework was the
top-performing entry in the MICCAI 2013 Multimodal Brain Tumor
Segmentation challenge and, to our knowledge, is the only entry for
both challenge years (2012 \& 2013) which has been made publicly
available.
\end{abstract}

>>>>

\begin{abstract} 
Segmenting and quantifying gliomas from MRI is an important task for diagnosis, planning intervention, 
and for tracking tumor changes over time.
However, this task is complicated by the lack
of prior knowledge concerning tumor location, spatial extent, shape,
possible displacement of normal tissue, and intensity signature.
These factors limit the applicability of techniques with established
performance in related tasks such as normal brain tissue
segmentation.  To alleviate the limitations of traditional tissue
classification, we introduce a symmetric template-based framework for supervised
segmentation based on multiple modality intensity, geometry and asymmetry feature sets.  These features drive a supervised whole-brain and tumor segmentation
approach based on random forest-derived probabilities.  The
asymmetry-related features, in particular, 
demonstrate excellent discriminative properties within this framework. 
We also gain performance by alternately generating
probability maps from random forest models and feeding these maps 
into Markov random field regularized probabilistic segmentation.  This
strategy allows us to interface the supervised learning capabilities of the random forest
model with regularized probabilistic segmentation.  The newly
developed \textit{ANTsR} open source software package facilitates
the proposed methodology.  \textit{ANTsR} is a comprehensive interface between the
popular Advanced Normalization Tools (ANTs) and the \textit{R}
statistical project. \textit{ANTsR} integrates proven image analysis methods
for image registration, segmentation, bias correction, and
template building with \textit{R}'s statistical and machine
learning techniques and state-of-the-art visualization possibilities.  
The reported algorithmic framework was the
top-performing entry in the MICCAI 2013 Multimodal Brain Tumor
Segmentation challenge and, to our knowledge, is the only entry for
both challenge years (2012 \& 2013) which has been made publicly
available.
\end{abstract}
